Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-18 WRITEUP/ms.tex
minor note and text edit

\begin{abstract}
We study the properties of molecular cloud (MC) complexes in a prototypical galaxy (``\flower") at redshift $z\approx 6$ using cosmological zoom-in simulations.
%
We identify MCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
%
In \flower, MCs masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc. Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter (gas+stars), and using a more observationally accessible $\alpha_{\rm vir}$ analysis. We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of collapse.
%
%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
%higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
\AF{Abstract is a bit thin. Revise at the end}
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive black holes). Subsequent feedback replenishes and enriches the circumgalactic medium with part of this material. The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or cosmic web at early cosmic times. Back then, galaxies themselves are more gas-rich and their molecular fraction possibly higher compared to present-day galaxies.

@@

We include a chemical network including ${\rm e}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using a on-the-fly non-equilibrium formation of molecular hydrogen scheme following \citet{Pallottini17b}).

@@

For each of the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), we identify a set of MCs.
%
Scaling relations for the MCs identified in the accretion phase are shown in left panels of \Fig{larsons_single} and in the right
panels for the starburst phase.
%
Regardless of the H$_2$ density cuts adopted, the MCs are found to have consistently 
high turbulences and surface densities in both stages. These correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs. As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).

>>>>

\begin{abstract}
We study the properties of molecular cloud (MC) complexes in a prototypical galaxy (``Alth{\ae}a'') at redshift $z\approx 6$ using cosmological zoom-in simulations.
%
We identify MCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
%
In \flower, MCs masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc. Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter (gas+stars), and using a more observationally accessible $\alpha_{\rm vir}$ analysis. We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of collapse.
%
%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
%higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
\AF{Abstract is a bit thin. Revise at the end}
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\section{Introduction}
\DL{please igonre Fig 7 for now. Labels/markers in the AlphaVir plots in Fig 5,6 will be updated based on Jens Kauffman's comments} 
The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive black holes). Subsequent feedback replenishes and enriches the circumgalactic medium with part of this material. The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or cosmic web at early cosmic times. Back then, galaxies themselves are more gas-rich and their molecular fraction possibly higher compared to present-day galaxies.

@@

We include a chemical network including ${\rm e}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using a on-the-fly non-equilibrium formation of molecular hydrogen scheme following \citet{Pallottini17b}.

@@

For each of the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), we identify a set of MCs.
%
Scaling relations for the MCs identified in the accretion phase are shown in left panels of \Fig{larsons_single} and in the right
panels for the starburst phase.
% 
Some MCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure)
compared to the accretion phase. \DL{Is this significant enough to say something physical? If so, not immediately clear to me what cause the differences.}
%
Regardless of the H$_2$ density cuts adopted, MCs in both phases are found to have consistently 
high turbulences and surface densities. They correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs. As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).
